A Study on Penguins: A Minimal Reproducible Example

### 2024-08-22 01_Example/Manuscript.tex
Recreate output

\RequirePackage{longtable}
% \setlength\LTleft{0pt}
\RequirePackage{threeparttablex}

% % % \RequirePackage{rotating}
% \RequirePackage{threeparttablex}
% \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
% \DeclareDelayedFloatFlavor{sidewaystable}{table}
% \DeclareDelayedFloatFlavor{longtable}{table}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}

% %

@@

\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep

@@

\title{A Study on Penguins: A Minimal Reproducible Example}
\shorttitle{A Study on Penguins: A Minimal Reproducible Example}

@@

\date{Invalid Date}

\abstract{This document is a minimal, reproducible manuscript using the
penguins data set as an example.}
% 
\keywords{penguins, reproducibility, minimal, example}

\authornote{\par{\addORCIDlink{Josephine
Zerna}{0000-0003-2892-884X}}\par{\addORCIDlink{Christoph
Scheffel}{0000-0001-5963-9229}}
\par{ }
\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Josephine
Zerna:   conceptualization, writing; Christoph Scheffel:   project
administration, methodology}
\par{Correspondence concerning this article should be addressed
to Christoph Scheffel, Email: christoph\_scheffel@tu-dresden.de}
}

\makeatletter
\let\endoldlt\endlongtable
\def\endlongtable{
\hline
\endoldlt
}
\makeatother
\RequirePackage{longtable}
\DeclareDelayedFloatFlavor{longtable}{table}
% \RequirePackage{threeparttablex}
% \DeclareDelayedFloatFlavor{ThreePartTable}{table}

@@

@@

Penguins are fascinating creatures that inhabit various regions of the
Southern Hemisphere, including Antarctica and surrounding islands. The
study of penguins provides valuable insights into ecosystem dynamics,
climate change impacts, and evolutionary biology (Jones, 2018; Smith,
2020).

@@

\begin{table}

\caption{\label{tab:descriptive_statistics}Summary Statistics}
\centering
\begin{tabular}[t]{llllllllll}
\toprule
\multicolumn{1}{c}{species} & \multicolumn{3}{c}{Adelie} & \multicolumn{3}{c}{Chinstrap} & \multicolumn{3}{c}{Gentoo} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
Variable & N & Mean & SD & N & Mean & SD & N & Mean & SD\\
\midrule
island & 146 &  &  & 68 &  &  & 119 &  & \\
... Biscoe & 44 & 30\% &  & 0 & 0\% &  & 119 & 100\% & \\
... Dream & 55 & 38\% &  & 68 & 100\% &  & 0 & 0\% & \\
... Torgersen & 47 & 32\% &  & 0 & 0\% &  & 0 & 0\% & \\
bill\_length\_mm & 146 & 39 & 2.7 & 68 & 49 & 3.3 & 119 & 48 & 3.1\\
\addlinespace
bill\_depth\_mm & 146 & 18 & 1.2 & 68 & 18 & 1.1 & 119 & 15 & 0.99\\
flipper\_length\_mm & 146 & 190 & 6.5 & 68 & 196 & 7.1 & 119 & 217 & 6.6\\
body\_mass\_g & 146 & 3706 & 459 & 68 & 3733 & 384 & 119 & 5092 & 501\\
sex & 146 &  &  & 68 &  &  & 119 &  & \\
... female & 73 & 50\% &  & 34 & 50\% &  & 58 & 49\% & \\
\addlinespace
... male & 73 & 50\% &  & 34 & 50\% &  & 61 & 51\% & \\
year & 146 & 2008 & 0.81 & 68 & 2008 & 0.86 & 119 & 2008 & 0.79\\
\bottomrule
\end{tabular}
\end{table}

The t-test revealed a significant difference in bill lengths between
male and female penguins (\$t(\$329.29 \()=\) -6.67, \(p\) \textless{}
0.001). Female penguins (\(M=\) 42.1mm, \(SD=\) 4.9 mm) exhibited
shorter bill lengths compared to male penguins (\(M=\) 45.85mm, \(SD=\)
5.37 mm).

\begin{figure}[H]

\caption{Histogram with Scatter Plot of Bill Lengths by Sex}

{\centering \includegraphics{Manuscript_files/figure-pdf/bill_length_comparison-1.pdf}

@@

The significant difference in bill lengths between male and female
penguins suggests potential sexual dimorphism in this trait. This
finding aligns with previous research indicating differential foraging
strategies and resource partitioning between male and female penguins
(Brown, 2015; Wilson, 2019).

>>>>

\usepackage[bidi=default]{babel}
\babelprovide[main,import]{english}

% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}

\RequirePackage{longtable}
\RequirePackage{threeparttablex}

@@

%\newlength\Oldarrayrulewidth
%\newlength\Oldtabcolsep

@@

\title{A Study on Penguins: A Minimal Reproducible Example}

\shorttitle{A Study on Penguins: A Minimal Reproducible Example}

@@

\date{2024-08-22}

\abstract{This document is a minimal, reproducible manuscript using the
penguins data set as an example.}

\keywords{penguins, reproducibility, minimal, example}

\authornote{\par{\addORCIDlink{Josephine
Zerna}{0000-0003-2892-884X}}\par{\addORCIDlink{Christoph
Scheffel}{0000-0001-5963-9229}}

\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Josephine
Zerna:   conceptualization, writing; Christoph Scheffel:   project
administration, methodology}
\par{Correspondence concerning this article should be addressed
to Christoph Scheffel, Email: christoph\_scheffel@tu-dresden.de}
}

\makeatletter
\let\endoldlt\endlongtable
\def\endlongtable{
\hline
\endoldlt
}
\makeatother
\RequirePackage{longtable}
\DeclareDelayedFloatFlavor{longtable}{table}

@@

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

Penguins are fascinating creatures that inhabit various regions of the
Southern Hemisphere, including Antarctica and surrounding islands. The
study of penguins provides valuable insights into ecosystem dynamics,
climate change impacts, and evolutionary biology
(\citeproc{ref-jones2018}{Jones, 2018}; \citeproc{ref-smith2020}{Smith,
2020}).

@@

\begin{table}
\caption{Summary Statistics}\tabularnewline

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
cell{1}{3}={c=2,}{halign=c,},
cell{1}{5}={c=2,}{halign=c,},
cell{1}{7}={c=2,}{halign=c,},
column{1}={halign=l,},
column{2}={halign=l,},
column{3}={halign=r,},
column{4}={halign=r,},
column{5}={halign=r,},
column{6}={halign=r,},
column{7}={halign=r,},
column{8}={halign=r,},
row{1}={halign=c,},
hline{8}={1,2,3,4,5,6,7,8}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
&  & Adelie (N=146) &  & Chinstrap (N=68) &  & Gentoo (N=119) &  \\ \cmidrule[lr]{3-4}\cmidrule[lr]{5-6}\cmidrule[lr]{7-8}
&    & Mean & Std. Dev. & Mean & Std. Dev. & Mean & Std. Dev. \\ \midrule %% TinyTableHeader
bill\_length\_mm    &           & \num{38.8}   & \num{2.7}   & \num{48.8}   & \num{3.3}   & \num{47.6}   & \num{3.1}   \\
bill\_depth\_mm     &           & \num{18.3}   & \num{1.2}   & \num{18.4}   & \num{1.1}   & \num{15.0}   & \num{1.0}   \\
flipper\_length\_mm &           & \num{190.1}  & \num{6.5}   & \num{195.8}  & \num{7.1}   & \num{217.2}  & \num{6.6}   \\
body\_mass\_g       &           & \num{3706.2} & \num{458.6} & \num{3733.1} & \num{384.3} & \num{5092.4} & \num{501.5} \\
year                  &           & \num{2008.1} & \num{0.8}   & \num{2008.0} & \num{0.9}   & \num{2008.1} & \num{0.8}   \\
&           & N             & Pct.         & N             & Pct.         & N             & Pct.         \\
island                & Biscoe    & \num{44}     & \num{30.1}  & \num{0}      & \num{0.0}   & \num{119}    & \num{100.0} \\
& Dream     & \num{55}     & \num{37.7}  & \num{68}     & \num{100.0} & \num{0}      & \num{0.0}   \\
& Torgersen & \num{47}     & \num{32.2}  & \num{0}      & \num{0.0}   & \num{0}      & \num{0.0}   \\
sex                   & female    & \num{73}     & \num{50.0}  & \num{34}     & \num{50.0}  & \num{58}     & \num{48.7}  \\
& male      & \num{73}     & \num{50.0}  & \num{34}     & \num{50.0}  & \num{61}     & \num{51.3}  \\
\bottomrule
\end{tblr}
\end{table}

The t-test revealed a significant difference in bill lengths between
male and female penguins (\(t(329.29) = -6.67, p < 0\.001\)). Female
penguins (\(M = 42.1\,\mathrm{mm}, SD = 4.9\,\mathrm{mm}\)) exhibited
shorter bill lengths compared to male penguins
(\(M = 45.85\,\mathrm{mm}, SD = 5.37\,\mathrm{mm}\)).

\begin{figure}

\caption{\label{fig-bill-length-comparison}Scatter Plot of Bill Lengths
by Sex With Violin Plot Showing Quartiles}

\centering{

\includegraphics{Manuscript_files/figure-pdf/fig-bill-length-comparison-1.pdf}

@@

The significant difference in bill lengths between male and female
penguins suggests potential sexual dimorphism in this trait. This
finding aligns with previous research indicating differential foraging
strategies and resource partitioning between male and female penguins
(\citeproc{ref-brown2015}{Brown, 2015};
\citeproc{ref-wilson2019}{Wilson, 2019}).
